\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/badusb.tex
Update

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious \ac{USB} devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

@@

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited.
Based on the drawbacks introduced above, several defense mechanisms were
proposed. For example, GoodUSB~\cite{tian2015defending}
implemented a authorization procedure when a new device is plugged in and blocks other functions excepted authorized ones.

@@

\textbf{\ac{HID} Emulation Mode.} This mode majorly relies on the ``\ac{HID} Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such feedback channel largely strengthen the attack ability of \tool.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from \ac{USB} 3.x, our \tool implements a
full-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
programs and shows attacks in the mobile attack scenarios. Details can
be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Also, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

\textbf{Video Capture Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

When running in this mode, \tool passively processes the victim's video stream
and detect for ``valuable'' private data.  The data is considered as
``valuable'' or not is decided by a customized detector, we implemented a simple
payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

It is worth mentioning that \tool under this mode is completely passive, making
it hard to be detected. With different detector implemented, \tool
under this mode is capable of serving more purposes.

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid \ac{HID}
input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirect it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movement from the attacker
through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.

This mode enable attacker to perform delicate operations that are beyond
automation. Moreover, this mode provides a backdoor that does not require host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victim device
and provide a backdoor beyond detection of firewalls; however, this complete control
also comes with the price of high power consumption and risk of being detected
by the user.

>>>>

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious \ac{USB} devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

@@

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
%rubberducky2020} emulates as a HID device enabling various arbitrary execution
%attacks, fetching feedback from the victim is much more limited.
Based on the drawbacks introduced above, several defense mechanisms were
proposed. For example, GoodUSB~\cite{tian2015defending}
implemented an authorization procedure when a new device is plugged in and blocks other functions except authorized ones.

@@

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in the Figure\shuqing{fig 3 delete?}~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from \ac{USB} 3.x, our \tool implements a
fully-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
programs and shows attacks in the mobile attack scenarios. Details can
be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it achieves defense bypass and attack
feedback with video streaming.  
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Also, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

\textbf{Video Capture Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses the 
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device mistakenly treats \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

When running in this mode, \tool passively processes the victim's video stream
and detects ``valuable'' private data.  The data is considered as
``valuable'' or not by a customized detector. We implemented a simple
payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

It is worth mentioning that \tool under this mode is completely passive, making
it hard to be detected. With different detectors implemented, \tool
under this mode is capable of serving more purposes.

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only does
the victim's device treat \tool as an external display, but also a valid \ac{HID}
input source. Hence we can achieve complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirects it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movements from the attacker
through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.

This mode enables attacker to perform delicate operations that are beyond
automation. Moreover, this mode provides a backdoor that does not require a host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victims device
and provides a backdoor beyond detection of firewalls; however, this complete control
also comes with the price of high power consumption and risk of being detected
by the user.
